\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-11-24 docs/papers/sto/so.tex
FIXUP draft tentative changes

%FIXME copied from ../adjoint/adjoint.tex
\newcommand{\deltaD}{\delta^\textsc{d}}
\newcommand{\deltaK}{\delta^\textsc{k}}
\renewcommand{\d}{d}
\newcommand{\p}{\partial}
\newcommand{\cJ}{\mathcal{J}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cH}{\mathcal{H}}
\bmdefine{\vzero}{0}
\bmdefine{\vI}{I}
\bmdefine{\vnabla}{\nabla}
\bmdefine{\vtheta}{\theta}  % parameters
\bmdefine{\vvartheta}{\vartheta}  % relevant scales and factors to form
                                  % dimensionless features as NN inputs
\bmdefine{\vomega}{\omega}  % white noise modes
\bmdefine{\vk}{k}  % wavevectors
\bmdefine{\vx}{x}  % comoving and canonical coordinates
\bmdefine{\vq}{q}  % Lagrangian coordinates
\bmdefine{\vs}{s}  % displacements
\bmdefine{\vp}{p}  % canonical momenta
\bmdefine{\vv}{v}  % FIXME some velocities
\bmdefine{\va}{a}  % accelerations
\bmdefine{\vz}{z}  % states
\bmdefine{\vo}{o}  % observable
\bmdefine{\vf}{f}
\bmdefine{\vF}{F}
\bmdefine{\vDelta}{\Delta}
\bmdefine{\vLambda}{\Lambda}
\bmdefine{\vlambda}{\lambda}
\bmdefine{\vvarphi}{\varphi}
\bmdefine{\vxi}{\xi}  % x adjoint
\bmdefine{\vpi}{\pi}  % p adjoint
\bmdefine{\valpha}{\alpha}  % force vjp x gradient
\bmdefine{\vzeta}{\zeta}  % force vjp theta gradient
\newcommand{\lna}{\ln\!a}
\newcommand{\lnk}{\ln\!k}
\newcommand{\half}{\nicefrac12}
\newcommand{\As}{A_\mathrm{s}}
\newcommand{\ns}{n_\mathrm{s}}
\newcommand{\Omegam}{\Omega_\mathrm{m}}
\newcommand{\Omegab}{\Omega_\mathrm{b}}
\newcommand{\Mpc}{\mathrm{Mpc}}
\newcommand{\ic}{\mathrm{i}}
\newcommand{\linear}{\mathrm{lin}}
\newcommand{\tophat}{\mathrm{TH}}
\newcommand{\gauss}{\mathrm{G}}

@@

\begin{table}
  \centering
  \caption{Possible features that can affect force sharpening.
  All scales are then multiplied by the wavenumber $k$ to form dimensionless
  factors.}
  \label{tab:feat}
  \begin{tabular}{rl}
  \toprule
  type & feature \\
  \midrule
  & $R_\mathrm{d}$: RMS linear displacement \\
  \cmidrule(lr){2-2}
  & $R_P$: $\Delta_\linear^2(R_P^{-1}) \triangleq 1$ \\
  \cmidrule(lr){2-2}
  nonlinear scales & $R_\tophat$: $\sigma_\tophat^2(R_\tophat) \triangleq 1$ \\
  \cmidrule(lr){2-2}
  & $R_\gauss$: $\sigma_\gauss^2(R_\gauss) \triangleq 1$ \\
  \cmidrule(lr){2-2}
  & $\d R / \d\lna$: time derivatives of the above \\
  \midrule
  & particle spacing \\
  \cmidrule(lr){2-2}
  other scales & $l$: PM force mesh cell size \\
  \cmidrule(lr){2-2}
  & softening length \\
  \midrule
  & $G_m(a) \triangleq D_m(a) / a^m, m \in \{1, 2, \YL{3's?}\}$ \\
  \cmidrule(lr){2-2}
  & $\d\ln G_m / \d\lna$ \\
  \cmidrule(lr){2-2}
  dimensionless factors & $\Omegam(a)$ \\
  \cmidrule(lr){2-2}
  & $\d\ln\!H / \d\lna$ \\
  \cmidrule(lr){2-2}
  & $\Delta\lna$: time step size in $\lna$ \\
  \bottomrule
  \end{tabular}
  \end{table}

@@

\begin{table*}
  \centering
  \caption{Ranges of \GADGET\ and \pmwd\ configuration and cosmological
  parameters.
  Note that the grid ratio need next fast len to determine the mesh shape
  for fast FFT.
  Given the box size, the mesh shape determines the cell size.
  The softening parameter gives the ratio of the comoving softening length
  to the mean particle spacing.
  The curvature $\Omega_k$ is related to the separate universe simulation.
  We sample parameters applicable to \GADGET\ during data generation, and
  those applicable to \pmwd\ during training.
  \textsuperscript\dag{}The box size is determined jointly by the \pmwd\
  mesh shape and mesh cell size below, which are assumed to be sampled
  independently.
  \YL{I forgot why I wrote ``Mpc'' without the $h$ here.}
  \YZ{We are using ``Mpc/h'' in the code.}
  In practice, we sample one conditioned on the other and the box size.
  *Number of time steps from $a=1/16$ to $a=1+1/128$ (in order to cover the
  snapshot offset).
  }
  \label{tab:param}
  \begin{tabular}{lcccr}
  \toprule
  applicability & parameter & distribution & range & sampling \\
  \midrule
  & $128^3$ white noise & $\mathcal{N}(\vzero, \vI)$ & 512 realizations & MC \\
  \cmidrule(lr){2-5}
  & 121 snapshots, $a$ & uniform & [1/16, 1] & deterministic \\
  \cmidrule(lr){2-5}
  & box size in Mpc\YZ{/h}\textsuperscript\dag & log-trapezoidal & [25.6, 2560) \\
  \cmidrule(lr){2-4}
  & snapshot offset, $\Delta\!a$ & uniform & [0, 1/128) \\
  \cmidrule(lr){2-4}
  \GADGET\ & $\As \times 10^9$ & log-uniform & [1, 4) \\
  \cmidrule(lr){2-4}
  \& \pmwd\ & $\ns$ & log-uniform & [0.75, 1.25) & RQMC \\
  \cmidrule(lr){2-4}
  & $\Omegam$ & log-uniform & [1/5, 1/2) & see \autoref{fig:sobol} \\
  \cmidrule(lr){2-4}
  & $\Omegab / \Omegam$ & log-uniform & [1/8, 1/4) \\
  \cmidrule(lr){2-4}
  & $\Omega_k / (1 - \Omega_k)$ & uniform & [-1/3, 1/3) \\
  \cmidrule(lr){2-4}
  & $h$ & log-uniform & [0.5, 1) \\
  \cmidrule(lr){1-4}
  \GADGET\ & softening ratio & log-uniform & [1/50, 1/20) \\
  \cmidrule(lr){1-5}
  & mesh shape & log-uniform & [128, 512] \\
  \cmidrule(lr){2-4}
  \pmwd\ & mesh cell size in Mpc\YZ{/h} & log-uniform & [0.2, 5] & MC \\
  \cmidrule(lr){2-4}
  & number of time steps* & log-uniform & [10, 1000] \\
  \cmidrule(lr){1-4}
  training & loss grid offset in its own spacing & uniform & $[0, 1)^3$ \\
  \bottomrule
  \end{tabular}
  \end{table*}

We generate our target data for training and testing with the \GADGET\
simulation code \citep{GADGET-4}.
We run 512 \GADGET\ simulations that cover a wide range of
configurations and cosmological parameters, as listed in
\autoref{tab:param}.
Each simulation has $128^3$ particles and writes 121 snapshots linearly
spaced in scale factor from $1/16 + \Delta a$ to $1 + \Delta a$, with
spacing $1/128$.
$\Delta a$ is an offset, common for all snapshots in each simulation,
that varies as in \autoref{tab:param} and helps to sample different
alignment between snapshot and start/stop times.
In our \pmwd\ model, we generate the snapshot at an arbitrary given time using
the cubic Hermite interpolation, with more details in \autoref{sec:snapobs}.
The curvature $\Omega_k$ is related to the separate universe simulation
\citep{LiEtAl2014, WagnerEtAl2015}.
\YZ{We refer to this training dataset of 512 \GADGET\ simulations sampled with
Sobol sequence as \GSDATA.}
On average each \GADGET\ simulation takes roughly 2K CPU hours to run, and the
generation of the whole \GSDATA\ dataset consumes 1M CPU hours.
% to be compare with the speed of pmwd with SO

@@

The loss function is constructed by comparing the simulated field $\hat f$ with
the target field $f$.
\YL{
For a field $f$ in either Lagrangian or Eulerian space, we have thought
of 3 forms of MSE-inspired loss:
%
\begin{equation}
\cL_f = \frac1{N_a} \ln
  \frac{\sum_\vq \bigl[ \hat f(\vq) - f(\vq) \bigr]^2}
       {\sum_{\vq'} f(\vq')^2},
\end{equation}
%
where $N_a$ is the number of time steps it takes to generate the snapshot for
each iteration
(or with $\vq$ replaced by $\vx$ for Eulerian fields, or equivalently by
their Fourier wavevector $\vk$ in both cases).
%
\begin{equation}
\cL_f = \frac1{N_K N_a} \sum_{ij} \ln \biggl[
\frac{\sum_{\vk \in K_i} \bigl| \hat f(\vk, a_j) - f(\vk, a_j) \bigr|^2}
     {\sum_{\vk' \in K_i} | f(\vk', a_j)|^2} + \epsilon \biggr],
\end{equation}
%
where $\epsilon$ sets the relative threshold tolerance below which we
consider $\hat f$ in each $K$ accurate enough, and the gradients from
that bin unimportant.
%and
%%
%\begin{equation}
%\cL_f = \frac1{N_a} \ln \biggl[ \frac1{N_K} \sum_i
%\frac{\sum_{k \in K_i} w(\vk)
%      \bigl| \hat f(\vk) - f(\vk) \bigr|^2}
%     {\sum_{k' \in K_i} |f(\vk')|^2} \biggl].
%\end{equation}
%%
Then the question is which loss we should use for which $f$, to get
stable and robust results, e.g., no bump for large or small boxes.
To further limit our scope in this paper, we should probably only
consider $f \in \{\vs, \delta\}$, and optionally the Lagrangian particle
velocity $\vv(\vq)$.
}

@@

\YL{Even though the log should be enough for adaptive optimizer and
fixed sim config, this may create problem when training on all config at
the same time. So normalizations inside the log is added above and
below.}

However, in the Eulerian space, an MSE loss is dominated by the small
scale modes.
In this work we choose uniform weights in the scale space on the
relative MSE.
We bin the modes logarithmically by \nicefrac13 octave in scale, with
the $i$-th $k$-bin $K_i \triangleq [k_i, k_{i+1})$, where $k_i =
2^{1+i/3} \pi / L$.
Our loss on the overdensity field $\delta$ sums up its MSE relative to
the target field power in logarithmic bins:
%
\begin{equation}
\cL_\delta = \frac1{N_K} \sum_i \ln
\frac{\sum_{k \in K_i} \bigl| \hat\delta(\vk) - \delta(\vk) \bigr|^2}
     {\sum_{k' \in K_i} |\delta(\vk')|^2},
\end{equation}
%
\begin{equation}
\cL_\delta = \frac1{N_K} \sum_i
\frac{\sum_{k \in K_i} w(\vk)
      \bigl| \hat\delta(\vk) - \delta(\vk) \bigr|^2}
     {\sum_{k' \in K_i} |\delta(\vk')|^2},
\end{equation}
%
where $N_K$ is the number of $k$-bins and $w(\vk)$ is a nonnegative
factor that suppresses the high $k$ contribution in Eulerian fields such
as the density field (with $w=1$ for the Lagrangian displacement field).
This is because a PM solver gradually loses small scale information step
by step, and without $w$ setting the priority, the loss function could
encourage the network to fit the small scales at the cost of the
intermediate scales.
Note that $\cL_\vs$ is on the displacement field $\vs(\vq)$ in the
Lagrangian space, while the density field is in the Eulerian space:
%
\begin{equation}
1 + \delta(\vx) = \int\!\d^3\vq\, \deltaD[ \vx - \vq - \vs(\vq)],
\end{equation}
%
which we compute by scattering particles to the choice of grid for loss.

@@

\vspace{1em}
\textit{\large Data Availability:}
\YZ{Do we make the \GSDATA\ data public?}

>>>>

%FIXME copied from ../adjoint/adjoint.tex
\newcommand{\deltaD}{\delta^\textsc{d}}
\newcommand{\deltaK}{\delta^\textsc{k}}
\renewcommand{\d}{d}
\newcommand{\p}{\partial}
\newcommand{\cJ}{\mathcal{J}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cH}{\mathcal{H}}
\bmdefine{\vzero}{0}
\bmdefine{\vI}{I}
\bmdefine{\vnabla}{\nabla}
\bmdefine{\vtheta}{\theta}  % parameters
\bmdefine{\vvartheta}{\vartheta}  % relevant scales and factors to form
                                  % dimensionless features as NN inputs
\bmdefine{\vomega}{\omega}  % white noise modes
\bmdefine{\vk}{k}  % wavevectors
\bmdefine{\vx}{x}  % comoving and canonical coordinates
\bmdefine{\vq}{q}  % Lagrangian coordinates
\bmdefine{\vs}{s}  % displacements
\bmdefine{\vp}{p}  % canonical momenta
\bmdefine{\vv}{v}  % FIXME some velocities
\bmdefine{\va}{a}  % accelerations
\bmdefine{\vz}{z}  % states
\bmdefine{\vo}{o}  % observable
\bmdefine{\vf}{f}
\bmdefine{\vF}{F}
\bmdefine{\vDelta}{\Delta}
\bmdefine{\vLambda}{\Lambda}
\bmdefine{\vlambda}{\lambda}
\bmdefine{\vvarphi}{\varphi}
\bmdefine{\vxi}{\xi}  % x adjoint
\bmdefine{\vpi}{\pi}  % p adjoint
\bmdefine{\valpha}{\alpha}  % force vjp x gradient
\bmdefine{\vzeta}{\zeta}  % force vjp theta gradient
\newcommand{\lna}{\ln\!a}
\newcommand{\lnk}{\ln\!k}
\newcommand{\half}{\nicefrac12}
\newcommand{\As}{A_\mathrm{s}}
\newcommand{\ns}{n_\mathrm{s}}
\newcommand{\Omegam}{\Omega_\mathrm{m}}
\newcommand{\Omegab}{\Omega_\mathrm{b}}
\newcommand{\OmegaK}{\Omega_K}
\newcommand{\Mpc}{\mathrm{Mpc}}
\newcommand{\ic}{\mathrm{i}}
\newcommand{\f}{\mathrm{f}}
\newcommand{\linear}{\mathrm{lin}}
\newcommand{\tophat}{\mathrm{TH}}
\newcommand{\gauss}{\mathrm{G}}

@@

\begin{table}
  \centering
  \caption{Possible features that can affect force sharpening.
  All scales are then multiplied by the wavenumber $k$ to form dimensionless
  factors.}
  \label{tab:feat}
  \begin{tabular}{rl}
  \toprule
  type & feature \\
  \midrule
  & $R_\mathrm{d}$: RMS linear displacement \\
  \cmidrule(lr){2-2}
  & $R_P$: $\Delta_\linear^2(R_P^{-1}) \triangleq 1$ \\
  \cmidrule(lr){2-2}
  nonlinear scales & $R_\tophat$: $\sigma_\tophat^2(R_\tophat) \triangleq 1$ \\
  \cmidrule(lr){2-2}
  & $R_\gauss$: $\sigma_\gauss^2(R_\gauss) \triangleq 1$ \\
  \cmidrule(lr){2-2}
  & $\d R / \d\lna$: time derivatives of the above \\
  \midrule
  & particle spacing \\
  \cmidrule(lr){2-2}
  other scales & $l$: PM force mesh cell size \\
  \cmidrule(lr){2-2}
  & softening length \\
  \midrule
  & $G_m(a) \triangleq D_m(a) / a^m, m \in \{1, 2, \YL{3's?}\}$ \\
  \cmidrule(lr){2-2}
  & $\d\ln G_m / \d\lna$ \\
  \cmidrule(lr){2-2}
  dimensionless factors & $\Omegam(a), \YL{\OmegaK(a)}$ \\
  \cmidrule(lr){2-2}
  & $\d\ln\!H / \d\lna$ \\
  \cmidrule(lr){2-2}
  & $\Delta\lna$: time step size in $\lna$\YL{. Now this can be an important feature with varying $a_\ic$}\\
  \bottomrule
  \end{tabular}
  \end{table}

@@

\begin{table*}
  \centering
  \caption{Ranges of \GADGET\ and \pmwd\ configuration and cosmological
  parameters.
  Note that the grid ratio need next fast len to determine the mesh shape
  for fast FFT.
  Given the box size, the mesh shape determines the cell size.
  The softening parameter gives the ratio of the comoving softening length
  to the mean particle spacing.
  The curvature $\OmegaK$ is related to the separate universe simulation.
  We sample parameters applicable to \GADGET\ during data generation, and
  those applicable to \pmwd\ during training.
  \YL{(I forgot why I wanted to sample mesh shape and mesh cell size...
  Now it seems more natural to me to have the ptcl spacing sampled
  uniformly instead...)}
  }
  \label{tab:param}
  \begin{tabular}{lcccr}
  \toprule
  applicability & parameter & distribution & range & sampling \\
  \midrule
  & $128^3$ white noise & $\mathcal{N}(\vzero, \vI)$ & 512 realizations & MC \\
  \cmidrule(lr){2-5}
  & box size in Mpc$/h$ & \YL{log-uniform} & [25.6, 2560) \\
  \cmidrule(lr){2-4}
  & snapshot offset & uniform & (0, 1] \\
  \cmidrule(lr){2-4}
  \GADGET\ & $\As \times 10^9$ & log-uniform & [1, 4) \\
  \cmidrule(lr){2-4}
  \& \pmwd\ & $\ns$ & log-uniform & [0.75, 1.25) & RQMC \\
  \cmidrule(lr){2-4}
  & $\Omegam$ & log-uniform & [1/5, 1/2) & see \autoref{fig:sobol} \\
  \cmidrule(lr){2-4}
  & $\Omegab / \Omegam$ & log-uniform & [1/8, 1/4) \\
  \cmidrule(lr){2-4}
  & $\OmegaK / (1 - \OmegaK)$ & uniform & [-1/3, 1/3) \\
  \cmidrule(lr){2-4}
  & $h$ & log-uniform & [0.5, 1) \\
  \cmidrule(lr){1-4}
  \GADGET\ & softening ratio & log-uniform & [1/50, 1/20) \\
  \cmidrule(lr){1-5}
  \pmwd\ & mesh shape & log-uniform & [128, 512] & MC \\
  \cmidrule(lr){2-4}
  \cmidrule(lr){1-4}
  training & loss grid offset & uniform & $[0, 1)^3$ \\
  \bottomrule
  \end{tabular}
  \end{table*}

We generate our target data for training and testing with the \GADGET\
simulation code \citep{GADGET-4}.
We run 512 \GADGET\ simulations that cover a wide range of
configurations and cosmological parameters, as listed in
\autoref{tab:param}.
\YL{
Each simulation evolves $128^3$ particles from the initial time $a_\ic$
to the final time $a_\f=1$, saving 64 snapshots linearly spaced in scale
factor from $a_\ic + \gamma \Delta a$ to $1 - (1 - \gamma) \Delta a$.
We determine $a_\ic$ for each configuration depending on its cosmology
and mean particle spacing \citep{MichauxEtAl2021}, \YL{(YL elaborate why and how here.)} which then sets the
snapshot spacing $\Delta a = (1 - a_\ic) / 64$.
To sample different alignment between the snapshots and the start/stop
times and avoid possible related numerical errors in \pmwd, we introduce
a fractional random offset $\gamma$ that varies between 0 and 1 for
different simulations.
}
In our \pmwd\ model, we generate the snapshot at an arbitrary given time using
the cubic Hermite interpolation, with more details in \autoref{sec:snapobs}.
The curvature $\OmegaK$ is related to the separate universe simulation
\citep{LiEtAl2014, WagnerEtAl2015}.
\YZ{We refer to this training dataset of 512 \GADGET\ simulations sampled with
Sobol sequence as \GSDATA.}
On average each \GADGET\ simulation takes roughly 2K CPU hours to run, and the
generation of the whole \GSDATA\ dataset consumes 1M CPU hours.
% to be compare with the speed of pmwd with SO

\YL{
In this work, we train \pmwd\ using $XXX$ time steps from $a_\ic$ to
$a_\f$, generate snapshots at the same times as in \GADGET, and compare
them in the loss function.
Although the number of time steps are fixed here, we emphasize that our
spatial optimization of course also applies for different number of time
steps, which we will explore, together with the optimal choice of time
variable, in a follow-up work on the temporal optimization.
}

@@

The loss function is constructed by comparing the simulated field $\hat f$ with
the target field $f$.
\YL{
For a field $f$ in either Lagrangian or Eulerian space%, we have thought
%of 3 forms of MSE-inspired loss:
%%
%\begin{equation}
%\cL_f = \frac1{N_a} \ln
%  \frac{\sum_\vq \bigl[ \hat f(\vq) - f(\vq) \bigr]^2}
%       {\sum_{\vq'} f(\vq')^2},
%\end{equation}
%%
%where $N_a$ is the number of time steps it takes to generate the snapshot for
%each iteration
%(or with $\vq$ replaced by $\vx$ for Eulerian fields, or equivalently by
%their Fourier wavevector $\vk$ in both cases).
%
\begin{equation}
\cL_f = \frac1{N_K N_a} \sum_{ij} \ln \biggl[
\frac{\sum_{\vk \in K_i} \bigl| \hat f(\vk, a_j) - f(\vk, a_j) \bigr|^2}
     {\sum_{\vk' \in K_i} | f(\vk', a_j)|^2} + \epsilon \biggr],
\end{equation}
%
where $N_a$ is the number of snapshots and $N_K$ is the number of
$k$-bins.
$\epsilon$ sets the relative threshold tolerance, below which we
consider $\hat f$ in each $K$ accurate enough and the gradients from
that bin less important.
%and
%%
%\begin{equation}
%\cL_f = \frac1{N_a} \ln \biggl[ \frac1{N_K} \sum_i
%\frac{\sum_{k \in K_i} w(\vk)
%      \bigl| \hat f(\vk) - f(\vk) \bigr|^2}
%     {\sum_{k' \in K_i} |f(\vk')|^2} \biggl].
%\end{equation}
%%
%Then the question is which loss we should use for which $f$, to get
%stable and robust results, e.g., no bump for large or small boxes.
%To further limit our scope in this paper, we should probably only
%consider $f \in \{\vs, \delta\}$, and optionally the Lagrangian particle
%velocity $\vv(\vq)$.
We can use $f \in \{\vs(\vq), \delta(\vx), \vv(\vq), (1+\delta)\vv(\vx),
(1+\delta)\vv\vv(\vx)\}$.
}

@@

%\YL{Even though the log should be enough for adaptive optimizer and
%fixed sim config, this may create problem when training on all config at
%the same time. So normalizations inside the log is added above and
%below.}

However, in the Eulerian space, an MSE loss is dominated by the small
scale modes.
In this work we choose uniform weights in the scale space on the
relative MSE.
We bin the modes logarithmically by \nicefrac13 octave in scale, with
the $i$-th $k$-bin $K_i \triangleq [k_i, k_{i+1})$, where $k_i =
2^{1+i/3} \pi / L$.
Our loss on the overdensity field $\delta$ sums up its MSE relative to
the target field power in logarithmic bins:
%
\begin{equation}
\cL_\delta = \frac1{N_K} \sum_i \ln
\frac{\sum_{k \in K_i} \bigl| \hat\delta(\vk) - \delta(\vk) \bigr|^2}
     {\sum_{k' \in K_i} |\delta(\vk')|^2},
\end{equation}
%
\begin{equation}
\cL_\delta = \frac1{N_K} \sum_i
\frac{\sum_{k \in K_i} w(\vk)
      \bigl| \hat\delta(\vk) - \delta(\vk) \bigr|^2}
     {\sum_{k' \in K_i} |\delta(\vk')|^2},
\end{equation}
%
where $N_K$ is the number of $k$-bins and $w(\vk)$ is a nonnegative
factor that suppresses the high $k$ contribution in Eulerian fields such
as the density field (with $w=1$ for the Lagrangian displacement field).
This is because a PM solver gradually loses small scale information step
by step, and without $w$ setting the priority, the loss function could
encourage the network to fit the small scales at the cost of the
intermediate scales.
Note that $\cL_\vs$ is on the displacement field $\vs(\vq)$ in the
Lagrangian space, while the density and momentum fields are in the
Eulerian space:
%
\begin{align}
1 + \delta(\vx) &= \int\!\d^3\vq\,
  \deltaD[ \vx - \vq - \vs(\vq)], \nonumber\\
(1 + \delta)\vv(\vx) &= \int\!\d^3\vq\,
  \vv(\vq) \deltaD[ \vx - \vq - \vs(\vq)], \nonumber\\
(1 + \delta)\vv\vv(\vx) &= \int\!\d^3\vq\,
  \vv\vv(\vq) \deltaD[ \vx - \vq - \vs(\vq)], \nonumber\\
\end{align}
%
which we compute by scattering particles to the choice of grid for loss.

@@

\vspace{1em}
\textit{\large Data Availability:}
We make the \GSDATA\ simulation data set public at ...
